---
title: "My Fancy Presentation"
author: "Jack Welch"
date: "July 2, 2017"
output:
   ioslides_presentation: 
      css: my.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

## My new slide

Some sample content.

*italicized text*

**Bold text**

`for (i %in% 1 : 10)`


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r echo=TRUE}
summary(cars)
```

```{r comment=""}
# Use blank character as comment
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

## Slide with figure options

```{r, echo=TRUE, fig.align='center', fig.cap="My AWESOME figure", fig.height=4}
library(stats)
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="MPG")
```

## My notes for publishing with GH-PAGES

### Simple way to preview HTML pages on GitHub

Prepend the URL to the raw HTML page with:
'http://htmlpreview.github.com/?https://github.com/koolwebdezign/data-products/blob/gh-pages/My_Fancy_Presentation.html'

### Use gh-pages branch

* git checkout --orphan gh-pages
* git push -u origin gh-pages
* delete the master branch

Prepend the URL with the RAW HTML:
'https://koolwebdezign.github.io/data-products/My_Fancy_Presentation.html'


